---
title: "Lab 00 - Hello IDS!"
author: "OLIVIA HARRIS"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Andrew", "Helen", "Adam", "Sarah", "Olivia", "Max"),
  github_username = c("pukklemaster", "helenrmiller", "adamlaycock", "sarahstewart142", "oliviaharris1", "MaxwellPohlman"),
  colour = c("mediumaquamarine", "thistle1", "forestgreen", "powderblue","violetred", "slategray3"),
  hobby = c("Knitting", "Croquet", "Guitar", "Swimming", "Netball", "Climbing"),
  favourite_number = c(7, 4, 6, 6, 4, 10),
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*Remove this text (including the stars), and add your answer for Exercise 18 here.*

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github_username", 
          y = "Favourite_number",
          title = "Usernames&FavouriteNumbers")
```

*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
